% Created 2018-02-07 Wed 23:10
\documentclass[12pt]{article}
                           \usepackage[all]{pabmacros}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage[normalem]{ulem}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage[nointegrals]{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{hyperref}
\tolerance=1000
\usepackage{amsmath}
\author{Paul Bryan}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Paul Bryan},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.2.2 (Org mode 8.3.5)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\section{D8 ii Publication List}
\label{sec:orgheadline3}
\subsection{Refereed Journal Articles}
\label{sec:orgheadline1}

\begin{itemize}
\item * Ben Andrews, \textbf{Paul Bryan}. \emph{Curvature bounds by isoperimetric comparison for normalized Ricci flow on the two-sphere}. Calc. Var. Partial Differential Equations 39, 419--428, 2010.
\item * Ben Andrews, \textbf{Paul Bryan}. \emph{A comparison theorem for the isoperimetric profile under curve-shortening flow}. Comm. Anal. Geom. 19, 503--539, 2011.
\item * Ben Andrews, \textbf{Paul Bryan}. \emph{Curvature bound for curve shortening flow via distance comparison and a direct proof of Grayson's theorem}. J. Reine Angew. Math. 653, 179--187. 2011.
\item * \textbf{Paul Bryan}. \emph{Isoperimetric Comparison Techniques for Low Dimension Curvature Flows}. Ph.D. Thesis, Australian National University, 2012.
\item * \textbf{Paul Bryan} \emph{Curvature bounds via an isoperimetric comparison for Ricci flow on surfaces} Ann. Scuola Norm. Sup. Pisa Cl. Sci September 2016, Volume 16, Issue 3
\item * \textbf{Paul Bryan}, Janelle Louie \emph{Classification of Convex Ancient Solutions to Curve Shortening Flow on the Sphere} J. Geom. Anal. April 2016, Volume 26, Issue 2, 858--872
\item * \textbf{Paul Bryan}, Mohammad Ivaki, Julian Scheuer \emph{Harnack inequalities for evolving hypersurfaces on the sphere} Comm. Anal Geom. (Accepted) 2016 arXiv: [math.DG] (available at \url{http://arxiv.org/abs/1512.03374})
\end{itemize}

\subsection{Other Research Outputs}
\label{sec:orgheadline2}

\begin{itemize}
\item * \textbf{Paul Bryan}, Mohammad Ivaki, Julian Scheuer \emph{On the classification of ancient solutions to curvature flows on the sphere}, Submitted to \emph{Journal of the European Mathematical Society}, 2016. arXiv: [math.DG] (available at \url{http://arxiv.org/abs/1604.01694})
\item * \textbf{Paul Bryan}, Mohammad Ivaki \emph{Harnack estimate for mean curvature flow on the sphere} Submitted to \emph{Asian Journal of Mathematics}, 2015. arXiv: [math.DG] (available at \url{http://arxiv.org/abs/1508.02821})
\item \textbf{Paul Bryan}, Mohammad Ivaki, Julian Scheuer \emph{A unified flow approach to smooth, even $L_p$-Minkowski problems}, Submitted to \emph{Analysis \& PDE} 2016 arXiv: [math.DG] (available at \url{http://arxiv.org/abs/1512.03374})
\item Lashi Bandara, \textbf{Paul Bryan} \emph{Heat kernels and regularity for rough metrics on smooth manifolds}, Submitted to \emph{Studia Mathematica} 2018 arxiv: [math.DG] (available at \url{https://arxiv.org/abs/1712.09287})
\end{itemize}
\end{document}
